Reintroduction of resistant frogs facilitates landscape-scale recovery in the presence of a lethal fungal disease

### 2024-04-21 doc/manuscript/translocation_bioarxiv_SI.tex
Create final files for submission

We estimated survival and recruitment for each site using open
population CMR models based on \citep{joseph2018}. For each individual
in a superpopulation of real and psuedo-individuals, \(i=1, ..., M\) on
each survey \(j=1, ..., n_j\): \(o_{i, j} = 1\) if the individual was
not detected, and \(o_{i, j}=2\) if the individual was detected. Capture
histories of \(M\) individuals are modeled, although only \(N_s\)
individuals were captured. This parameter expanded data augmentation
allows us to capture the possibility that undetected individuals may
have recruited into the adult population \citep{royle2012}. Here, \(M\)
was chosen to be three times the number of observed individuals
(\(3N_s\)) to be considerably greater than our prior guess of \(N_s\).

@@

We computed yearly survival probabilities for translocated adults
\(\sigma_{A_T}\) and naturally recruited adults \(\sigma_{A_R}\) from
the posterior distribution of individual state trajectories derived from
mrmr CMR models. Although we observed yearly variability in adult
survival within a population, the magnitude of this variability was
small compared to among-population variability
(Fig. 2). Thus, we did not include
yearly within-population variability in adult survival in this analysis.
However, within a population there was substantial yearly variability in
the successful recruitment of adults, greater than what we would expect
from Poisson variability around a mean value. Therefore, we allowed for
yearly variability in the probability of year-1 juvenile survival and
recruitment (additional details provided in \textbf{Estimating model
parameters} below). We also could have included environmental
stochasticity in year-2 juvenile survival and recruitment
\(\sigma_{J_2}\), but our elasticity analysis (\textbf{Supporting
Information - Population viability modeling - Model analysis and
simulation}) showed that this parameter had little effect on host growth
rate relative to \(\sigma_{J_1}\) (Figure~\ref{fig-viability-supp}).

@@

To estimate the \(\sigma_{A_R}\), we used the posterior distribution of
predicted true states for naturally-recruited individuals (1=not
recruited, 2=alive, 3=dead, as described in \textbf{Supporting
Information - Frog population recovery - CMR model structure}), then
calculated the posterior probability of individuals surviving between
consecutive primary periods, conditional on being alive in the first
primary period (e.g., given a value of 2 (alive) in the first primary
period, how often was the value still 2 (alive) in the next primary
period compared to 3 (dead)) . This yielded posterior distributions for
survival probabilities between primary periods. However, because the
time interval between primary periods differed, the survival
probabilities between different consecutive primary periods were not
directly comparable. To address this, we converted the survival
probabilities between each consecutive primary period to per day death
rates, propagating the uncertainty from the posterior distributions. We
then took a weighted average of these death rates, weighted by the time
interval between primary periods, to get the average per day death rate
over the entire CMR survey. We converted this per day death rate \(d\)
back to a yearly survival probability using
\(\exp(-d \times 365 \text{ days})\). We used the same procedure for
\(\sigma_{A_T}\) such that our estimates of average yearly survival
probability were comparable between \(\sigma_{A_R}\) and
\(\sigma_{A_T}\).

@@

Third, we defined a version of the model with demographic and
environmental stochasticity, where environmental stochasticity was
represented by among-year variability in \(\sigma_{J_1}\). We used this
model to simulate a one-time introduction of 40 translocated adult
frogs. We ran this simulation 1000 times for each population and
computed the probability of a population becoming extinct after 50 years
given the observed parameter values and environmental stochasticity in
\(\sigma_{J_1}\). We varied the mean recruitment probability
\(\sigma_{J_1}\) from 0 and 0.25 and drew values of \(\sigma_{J_1}\)
each year from a beta distribution with a dispersion parameter of
\(\phi = 2\) (when \(\sigma_{J_1} = 0.5\) and \(\phi = 2\) the beta
distribution is uniform between 0 and 1). Using different values of
\(\phi\) does not qualitatively change the existence of distinct
extinction dynamics between populations with \(\sigma_{A_R} < 0.5\) and
those with \(\sigma_{A_R} > 0.5\). However, increasing yearly
variability in \(\sigma_{J_1}\) increases extinction risk for all
populations. For example, if we set \(\phi = 0.001\), such that in a
given year essentially either all year-1 juveniles survive or all of
them die, populations with \(\sigma_{A_R} > 0.5\) need to have
\(\sigma_{J_1}\) greater than 0.2 to have a 50-year extinction
probability of less 50\%. Because we do not pit tag juveniles, we do not
have CMR estimates for \(\sigma_{J_1}\) or \(\phi\). However, based on
qualitative and semi-quantitative field observations over 25 years, a
value of \(\sigma_{J_1} = 0.25\) in the presence of Bd is probably a
reasonable estimate for many populations. Thus, we expect our model
predictions to be conservative with regards to population recovery.

@@

Our study design, in which we compared frog genomes in naive and
recovering populations, required sampling populations across the range
of MYL frogs in the southern Sierra Nevada. This is due to the fact that
very few MYL frog populations remain in the naive state, and those that
do are scattered across a wide latitudinal range, from Yosemite National
Park in the north to southern Kings Canyon National Park in south. To
minimize potential confounding effects caused by known variation in frog
genotypes across latitude \citep{byrne2023}, we selected sampling sites
such that both population types were represented across similar
latitudinal ranges (Fig. 5).

@@

In \textbf{Results-Frog evolution in response to Bd}, we describe the
stringent set of outlier variants (identified using a
Bonferroni-corrected p-value of 0.01). A liberal set of outlier
variants, identified using a Bonferroni-corrected p-value of 0.05,
included 38 outliers (35 SNPs and 3 INDELS) from 30 distinct genes
across 16 contigs. We used this liberal set to determine if any GO
biological functions, molecular functions, or cellular processes were
overrepresented. To do this, we retrieved the BLAST hits and mapped GO
terms for each gene in our targeted transcriptome. We then conducted a
statistical overrepresentation test (Fisher's exact test) using Blast2GO
\citep{conesa2005} to compare the 30 unique outlier genes to the
complete set of genes in our target transcriptome. We repeated this
process for the set of 35 genes located in the 9 shared regions of the
\emph{F\textsubscript{ST}} and \(\pi_{diff}\) splined windows.

@@

To characterize general patterns of genetic diversity between naive and
recovering populations, we conducted three analyses. First, we
calculated heterozygosity for each sampled frog using VCFtools
\citep{danecek2011}. Second, to characterize genome-wide patterns of
diversity, we used VCFtools to calculate nucleotide diversity (\(\pi\))
in 100kb sliding windows along the genome for each population. Third, we
calculated average \(\pi\) per population within each of the 9 outlier
windows identified in the splined window analysis.

Average individual-level heterozygosity and genome-wide population-level
\(\pi\) were similar between the naive and recovering groups
(Figure~\ref{fig-violinplot-heterozy};
Figure~\ref{fig-boxplot-genomewide-pi-by-pop}). Within each of the 9
outlier windows, average \(\pi\) shows considerable variation between
populations (Figure~\ref{fig-boxplot-pi-by-windowpop}) and no obvious
patterns between the naive and recovering groups.

@@

{\centering \includegraphics[width=0.7\textwidth]{figures/bdload_beforeafter.png}

@@

\caption{\label{fig-compare_surv_probs}Comparison of average yearly
adult survival probabilities for adults translocated to each of 3 sites
versus adults that were naturally recruited at each site (as a result of
reproduction by translocated frogs). In contrast to
Fig. 2, these are not survival
probabilities from the first year following translocation, but instead
represent averaged survival probabilities across multiple years and
cohorts. Points are median estimates and error bars give the 95\%
uncertainty intervals around the estimates, accounting for yearly
variation in survival probabilities. All estimates were derived using
the mrmr package, and the methods for calculation are described in
\textbf{Supporting Information - Population viability modeling -
Estimating model parameters}.}

@@

{\centering \includegraphics[width=0.60\textwidth]{figures/pop_viability_figures_for_supp.jpg}

@@

\caption{\label{fig-viability-supp}Sensitivity analysis of the
stage-structured MYL frog model. A. Elasticity of \(\lambda\) with
changes in nine parameters: \(\sigma_{A_R}\) (yearly survival
probability of naturally recruited adults), \(F\) (number of eggs
produced by a female frog in a year that successfully hatch),
\(\sigma_{J_1}\) (yearly probability of survival of year-1 juveniles
that also affects recruitment), \(\sigma_{J_2}\) (yearly probability of
survival and recruitment of year-2 juveniles), \(p_{L_2}\) (probability
that year-2 tadpoles metamorph into juveniles), \(p_{J_1}\) (probability
that year-1 juveniles mature to adults), \(\sigma_{L_1}\) (survival
probability of year-1 tadpoles), \(\sigma_{L_2}\) (survival probability
of year-2 tadpoles), and \(\sigma_{L_3}\) (survival probability of
year-3 tadpoles). B. Sensitivity of \(\lambda\) with changes in the same
nine parameters. Note that \(F\) has different units than the other
parameters, which is why its sensitivity is low. Sensitivities of all
other parameters are comparable. We did not include \(p_{L_1}\) as this
parameter is generally 1 across the populations in this study (Table S1)
-- tadpoles spend at least a year as tadpoles before metamorphosing.
Elasticity and sensitivity is calculated at the default parameter values
for each population and \(\sigma_{J_1}\) = 0.09.}

@@

\caption{\label{fig-selectionresults}Results from the analysis of
individual variants, showing putative signatures of selection in
recovering MYL frog populations. (A) PCA calculated from binary SNPs
showing the genomic relationship of samples. Numeric labels and colors
match those in Fig. 5. Populations 1-7 are
\emph{R. sierrae} and populations 8 and 9 are \emph{R. muscosa}. (B)
qqplot showing observed and expected p-values for 148,307 SNPs and
INDELS. Dashed line shows p-value that identifies outliers. (C)
Manhattan plot showing p-value for each SNP. SNPs are sorted by genomic
position and contigs are sorted by size. Red line shows p-value that
identifies outliers. Outlier SNPs above this threshold are highlighted
and labeled. Bold labels indicate the presence of at least one
non-synonymous SNP in that gene.}

@@

{\centering \includegraphics[width=0.85\textwidth]{figures/synteny_figure.png}

@@

\caption{\label{fig-synteny-plot}Synteny plot showing conserved gene
order in \emph{Xenopus tropicalis} and \emph{Rana muscosa} for the
outlier region containing MHC Class I Classical and MHC Class III gene
regions. The plot was created with SimpleSynteny \citep{veltri2016}
using \emph{Xenopus tropicalis} Chromosome 8 (NC\_030684.2, genbank
accession GCA\_000004195.4) and \emph{Rana muscosa} Contig19. Asterices
indicate the location of SNP outliers in the TCF19 and VARS1 genes. Gap
sizes for each contig representation are labeled.}

@@

{\centering \includegraphics[width=0.85\textwidth]{figures/violin_plot_heterozy_by_group.png}

@@

\caption{\label{fig-violinplot-heterozy}Violin plots showing individual
heterozygosity for the Bd-naive and recovering populations included in
the frog evolution study. Individual data points are represented by
their corresponding site number (from
Fig. 5).}

@@

{\centering \includegraphics[width=0.85\textwidth]{figures/boxplot_genomewide_pi_by_pop.png}

@@

\caption{\label{fig-boxplot-genomewide-pi-by-pop}For each study
population in the frog evolution study (from
Fig. 5), boxplots showing nucleotide
diversity (\(\pi\)) within 100kb sliding windows along the genome. The
y-axis has been log\textsubscript{10}-transformed for display purposes.
Sites are color-coded as ``Bd-naive'' or ``recovering'', and vertical
dashed lines show the genetic breaks between frog populations as
described in Figure~\ref{fig-selectionresults} A).}

@@

{\centering \includegraphics[width=0.85\textwidth]{figures/boxplot_pi_by_windowpop.png}

@@

\caption{\label{fig-boxplot-pi-by-windowpop}For each of the 9 outlier
windows identified by the overlapping splined windows for
\emph{F\textsubscript{ST}} and \(\pi\), boxplots showing average \(\pi\)
for naive and recovering populations. The corresponding gene annotations
for each window are as follows: (1) C6, C7, (2) DDX10, ZBTB24, (3)
SULTR-like, TRAF3IP2, VGLL3, EXOC1, (4) FLOT1, TUBB, MDC1, CCHCR1,
TCF19, HSP70, LSM2, VARS1, (5) GCC2, CFAP251, PEG10, (6) ERO1A, GVINP1,
(7) PPP1R12A, TSPAN4, PAWR, MFRP, MAX, PPP6R3, (8) C6H5ORF22, PKS6,
BSPRY, MPV17, and (9) CAD, ATRAID, GPN1.}

@@

{\centering \includegraphics[width=0.85\textwidth]{figures/ave_pi_per_site_yose.png}

@@

\caption{For each study population located in Yosemite National Park
(populations 1-4 shown in Site Map), average \(\pi\) for the 9 outlier
windows (panels A-I) identified in the splined window analysis.
Populations within Yosemite are the focus because they are the most
relevant to the translocated populations described in the paper: donor
populations 1 and 4 were the source of frogs for 20 of the 24
translocations and the donor population for the remaining four
translocations is located adjacent to populations 3 and 4. Bars are
color-coded by population category (naive, recovering), and gene
annotations within each window are listed above each panel. Gene regions
described in the paper are in panel A (Complement C6,C7), panel E
(GVINP1), and panel F (extended MHC region that includes two SNPs
identified by the GEMMA analysis in genes TCF19 and VARS1, indicated by
an *). In the Site Map, the four populations included in panels A-I are
color-coded by population category, and dashed lines delineate the
genetic clusters as defined in Figure~\ref{fig-selectionresults}.}

>>>>

We estimated survival and recruitment for each site using open
population CMR models based on \citep{joseph2018}. For each individual
in a superpopulation of real and psuedo-individuals, \(i=1, ..., M\) on
each survey \(j=1, ..., n_j\): \(o_{i, j} = 1\) if the individual was
not detected, and \(o_{i, j}=2\) if the individual was detected. Capture
histories of \(M\) individuals are modeled, although only \(N_s\)
individuals were captured. This parameter expanded data augmentation
allows us to account for the possibility that undetected individuals may
have recruited into the adult population \citep{royle2012}. Here, \(M\)
was chosen to be three times the number of observed individuals
(\(3N_s\)) to be considerably greater than our prior guess of \(N_s\).

@@

We computed yearly survival probabilities for translocated adults
\(\sigma_{A_T}\) and naturally recruited adults \(\sigma_{A_R}\) from
the posterior distribution of individual state trajectories derived from
mrmr CMR models. Although we observed yearly variability in adult
survival within a population, the magnitude of this variability was
small compared to among-population variability
(Figure 2). Thus, we did not include
yearly within-population variability in adult survival in this analysis.
However, within a population there was substantial yearly variability in
the successful recruitment of adults, greater than what we would expect
from Poisson variability around a mean value. Therefore, we allowed for
yearly variability in the probability of year-1 juvenile survival and
recruitment (additional details provided in \textbf{Estimating model
parameters} below). We also could have included environmental
stochasticity in year-2 juvenile survival and recruitment
\(\sigma_{J_2}\), but our elasticity and sensitivity analysis (see
below, \textbf{Model analysis and simulation}) showed that this
parameter had little effect on host growth rate relative to
\(\sigma_{J_1}\) (Figure~\ref{fig-viability-supp}).

@@

To estimate the \(\sigma_{A_R}\), we used the posterior distribution of
predicted true states for naturally-recruited individuals (1=not
recruited, 2=alive, 3=dead, as described in \textbf{Supporting
Information - Frog population recovery - CMR model structure}), then
calculated the posterior probability of individuals surviving between
consecutive primary periods, conditional on being alive in the first
primary period (e.g., given a value of 2 (alive) in the first primary
period, how often was the value still 2 (alive) in the next primary
period compared to 3 (dead)). This yielded posterior distributions for
survival probabilities between primary periods. However, because the
time interval between primary periods differed, the survival
probabilities between different consecutive primary periods were not
directly comparable. To address this, we converted the survival
probabilities between each consecutive primary period to per day death
rates, propagating the uncertainty from the posterior distributions. We
then took a weighted average of these death rates, weighted by the time
interval between primary periods, to get the average per day death rate
over the entire CMR survey. We converted this per day death rate \(d\)
back to a yearly survival probability using
\(\exp(-d \times 365 \text{ days})\). We used the same procedure for
\(\sigma_{A_T}\) such that our estimates of average yearly survival
probability were comparable between \(\sigma_{A_R}\) and
\(\sigma_{A_T}\).

@@

Third, we defined a version of the model with demographic and
environmental stochasticity, where environmental stochasticity was
represented by among-year variability in \(\sigma_{J_1}\). We used this
model to simulate a one-time introduction of 40 translocated adult
frogs. We ran this simulation 1000 times for each population and
computed the probability of a population becoming extinct after 50 years
given the observed parameter values and environmental stochasticity in
\(\sigma_{J_1}\). We varied the mean recruitment probability
\(\sigma_{J_1}\) from 0 and 0.25 and drew values of \(\sigma_{J_1}\)
each year from a beta distribution with a dispersion parameter of
\(\phi = 2\) (when \(\sigma_{J_1} = 0.5\) and \(\phi = 2\) the beta
distribution is uniform between 0 and 1). Using different values of
\(\phi\) does not qualitatively change the existence of distinct
extinction dynamics between populations with \(\sigma_{A_R} < 0.5\) and
those with \(\sigma_{A_R} > 0.5\). However, increasing yearly
variability in \(\sigma_{J_1}\) increases extinction risk for all
populations. For example, if we set \(\phi = 0.001\), such that in a
given year essentially either all year-1 juveniles survive or all of
them die, populations with \(\sigma_{A_R} > 0.5\) need to have
\(\sigma_{J_1}\) greater than 0.2 to have a 50-year extinction
probability of less 50\%. Because we do not PIT tag juveniles, we do not
have CMR estimates for \(\sigma_{J_1}\) or \(\phi\). However, based on
qualitative and semi-quantitative field observations over 25 years, a
value of \(\sigma_{J_1} = 0.25\) in the presence of Bd is probably a
reasonable estimate for many populations. Thus, we expect our model
predictions to be conservative with regards to population recovery.

@@

Our study design, in which we compared frog genomes in naive and
recovering populations, required sampling populations across the range
of MYL frogs in the southern Sierra Nevada. This is due to the fact that
very few MYL frog populations remain in the naive state, and those that
do are scattered across a wide latitudinal range, from Yosemite National
Park in the north to southern Kings Canyon National Park in south. To
minimize potential confounding effects caused by known variation in frog
genotypes across latitude \citep{byrne2023}, we selected sampling sites
such that both population types were represented across similar
latitudinal ranges (Figure 5).

@@

In \textbf{Results-Frog genome evolution}, we describe the stringent set
of outlier variants (identified using a Bonferroni-corrected p-value of
0.01). A liberal set of outlier variants, identified using a
Bonferroni-corrected p-value of 0.05, included 38 outliers (35 SNPs and
3 INDELS) from 30 distinct genes across 16 contigs. We used this liberal
set to determine if any GO biological functions, molecular functions, or
cellular processes were overrepresented. To do this, we retrieved the
BLAST hits and mapped GO terms for each gene in our targeted
transcriptome. We then conducted a statistical overrepresentation test
(Fisher's exact test) using Blast2GO \citep{conesa2005} to compare the
30 unique outlier genes to the complete set of genes in our target
transcriptome. We repeated this process for the set of 35 genes located
in the 9 shared regions of the \emph{F\textsubscript{ST}} and
\(\pi_{diff}\) splined windows.

@@

To characterize general patterns of genetic diversity between naive and
recovering populations, we conducted three analyses. First, we
calculated heterozygosity for each sampled frog using VCFtools
\citep{danecek2011}. Second, to characterize genome-wide patterns of
diversity, we used VCFtools to calculate nucleotide diversity (\(\pi\))
in 100kb sliding windows along the genome for each population. Third, we
calculated average \(\pi\) per population within each of the 9 shared
outlier regions identified in the splined window analysis. We compared
average \(\pi\) per population between naive and recovering population
types, and also for each naive and recovering population in Yosemite.
The latter comparison focused on Yosemite because these populations are
the most relevant to the translocated populations described in the
paper.

Average individual-level heterozygosity and genome-wide population-level
\(\pi\) were similar between the naive and recovering groups
(Figure~\ref{fig-violinplot-heterozy};
Figure~\ref{fig-boxplot-genomewide-pi-by-pop}). Within each of the 9
shared outlier regions, \(\pi\) shows considerable variation between
populations and no obvious patterns between the naive and recovering
populations (Figure~\ref{fig-boxplot-pi-by-regionpop}).

@@

{\centering \includegraphics[width=0.80\textwidth]{figures/bdload_beforeafter.png}

@@

\caption{\label{fig-compare_surv_probs}Comparison of average yearly
adult survival probabilities for adults translocated to each of 3 sites
versus adults that were naturally recruited at each site (as a result of
reproduction by translocated frogs). In contrast to
Figure 2, these are not survival
probabilities from the first year following translocation, but instead
represent averaged survival probabilities across multiple years and
cohorts. Points are median estimates and error bars give the 95\%
uncertainty intervals around the estimates, accounting for yearly
variation in survival probabilities. All estimates were derived using
the mrmr package, and the methods for calculation are described in
\textbf{Supporting Information - Population viability modeling -
Estimating model parameters}.}

@@

{\centering \includegraphics[width=0.95\textwidth]{figures/pop_viability_figures_for_supp.jpg}

@@

\caption{\label{fig-viability-supp}Sensitivity analysis of the
stage-structured MYL frog model. A. Elasticity of \(\lambda\) with
changes in nine parameters: \(\sigma_{A_R}\) (yearly survival
probability of naturally recruited adults), \(F\) (number of eggs
produced by a female frog in a year that successfully hatch),
\(\sigma_{J_1}\) (yearly probability of survival of year-1 juveniles
that also affects recruitment), \(\sigma_{J_2}\) (yearly probability of
survival and recruitment of year-2 juveniles), \(p_{L_2}\) (probability
that year-2 tadpoles metamorph into juveniles), \(p_{J_1}\) (probability
that year-1 juveniles mature to adults), \(\sigma_{L_1}\) (survival
probability of year-1 tadpoles), \(\sigma_{L_2}\) (survival probability
of year-2 tadpoles), and \(\sigma_{L_3}\) (survival probability of
year-3 tadpoles). B. Sensitivity of \(\lambda\) with changes in the same
nine parameters. Note that \(F\) has different units than the other
parameters, which is why its sensitivity is low. Sensitivities of all
other parameters are comparable. We did not include \(p_{L_1}\) as this
parameter is 1 across the populations in this study (Table S1) --
tadpoles spend at least a year as tadpoles before metamorphosing.
Elasticity and sensitivity is calculated at the default parameter values
for each population and \(\sigma_{J_1}\) = 0.09.}

@@

\caption{\label{fig-selectionresults}Results from the analysis of
individual variants, showing possible signatures of selection in
recovering MYL frog populations. (A) PCA calculated from binary SNPs
showing the genomic relationship of samples. Numeric labels and colors
match those in Figure 5. Populations 1-7 are
\emph{R. sierrae} and populations 8 and 9 are \emph{R. muscosa}. (B)
qqplot showing observed and expected p-values for 148,307 SNPs and
INDELS. Dashed line shows p-value that identifies outliers. (C)
Manhattan plot showing p-value for each SNP. SNPs are sorted by genomic
position and contigs are sorted by size. Red line shows p-value that
identifies outliers. Outlier SNPs above this threshold are highlighted
and labeled. Bold labels indicate the presence of at least one
non-synonymous SNP in that gene.}

@@

{\centering \includegraphics[width=0.95\textwidth]{figures/synteny_figure.png}

@@

\caption{\label{fig-synteny-plot}Synteny plot showing conserved gene
order in \emph{Xenopus tropicalis} and \emph{Rana muscosa} for the
outlier region containing MHC Class I Classical and MHC Class III gene
regions. The plot was created with SimpleSynteny \citep{veltri2016}
using \emph{Xenopus tropicalis} Chromosome 8 (NC\_030684.2, genbank
accession GCA\_000004195.4) and \emph{Rana muscosa} Contig19. Asterisks
indicate the location of SNP outliers in the TCF19 and VARS1 genes. Gap
sizes for each contig representation are labeled.}

@@

{\centering \includegraphics[width=0.85\textwidth]{figures/ave_pi_per_popn_yose.png}

@@

\caption{\label{fig-ave-pi-per-popn-yose}For each study population
located in Yosemite National Park (populations 1-4 shown in the map),
\(\pi\) for the 9 shared outlier regions identified in the splined
window analysis. Populations 1 and 4 were the source of frogs for 20 of
the 24 frog translocations, and the donor population for the remaining
four translocations is located adjacent to populations 3 and 4 (see also
Figure~\ref{fig-yosemap}). Bars are color-coded by population type
(naive, recovering). The corresponding gene annotations for each region
are as follows (gene regions described in the \textbf{Results} and
\textbf{Discussion} are indicated with an asterisk): (1) C6*, C7*, (2)
DDX10, ZBTB24, (3) SULTR-like, TRAF3IP2, VGLL3, EXOC1, (4) FLOT1, TUBB,
MDC1, CCHCR1, TCF19*, HSP70, LSM2, VARS1*, (5) GCC2, CFAP251, PEG10, (6)
ERO1A, GVINP1*, (7) PPP1R12A, TSPAN4, PAWR, MFRP, MAX, PPP6R3, (8)
C6H5ORF22, PKS6, BSPRY, MPV17, and (9) CAD, ATRAID, GPN1. Region 4 is
the extended MHC region that includes two SNPs identified by the GEMMA
analysis in genes TCF19 and VARS1. In the map, the four populations
included in panels 1-9 are color-coded by population type, and dashed
lines delineate the genetic clusters as defined in
Figure~\ref{fig-selectionresults}A.}

@@

{\centering \includegraphics[width=0.60\textwidth]{figures/violin_plot_heterozy_by_group.png}

@@

\caption{\label{fig-violinplot-heterozy}Violin plots showing individual
heterozygosity for the Bd-naive and recovering populations included in
the frog evolution study. Individual data points are represented by
their corresponding site number (from
Figure 5).}

@@

{\centering \includegraphics[width=0.70\textwidth]{figures/boxplot_genomewide_pi_by_pop.png}

@@

\caption{\label{fig-boxplot-genomewide-pi-by-pop}For each population in
the frog evolution study (Figure 5), boxplots
showing nucleotide diversity (\(\pi\)) within 100kb sliding windows
along the genome. The y-axis has been log\textsubscript{10}-transformed
for display purposes. Sites are color-coded as ``Bd-naive'' or
``recovering'', and vertical dashed lines show the genetic breaks
between frog populations as described in
Figure~\ref{fig-selectionresults}A).}

@@

{\centering \includegraphics[width=0.70\textwidth]{figures/boxplot_pi_by_regionpop.png}

@@

\caption{\label{fig-boxplot-pi-by-regionpop}For each of the 9 shared
outlier regions identified by the splined window analysis, boxplots
showing \(\pi\) values for naive and recovering populations. The
corresponding gene annotations for each region are as follows (gene
regions described in the \textbf{Results} and \textbf{Discussion} are
indicated with an asterisk): (1) C6*, C7*, (2) DDX10, ZBTB24, (3)
SULTR-like, TRAF3IP2, VGLL3, EXOC1, (4) FLOT1, TUBB, MDC1, CCHCR1,
TCF19*, HSP70, LSM2, VARS1*, (5) GCC2, CFAP251, PEG10, (6) ERO1A,
GVINP1*, (7) PPP1R12A, TSPAN4, PAWR, MFRP, MAX, PPP6R3, (8) C6H5ORF22,
PKS6, BSPRY, MPV17, and (9) CAD, ATRAID, GPN1.}
